Implementing a Capability Machine model into Iris

### 2020-01-11 prisc-2020-talk/slides.tex
altered the slides

\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{tikz}
\usetikzlibrary{matrix}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{IEEEtrantools}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage{longtable}
\usepackage{mathtools}

@@

\newcommand{\ra}[1] {
  \begin{tikzpicture}
        \node[draw,dashed] {#1};
    \end{tikzpicture}}

@@

\begin{frame}
\frametitle{Overview} % Table of contents slide, comment this block out to remove it
\tableofcontents[hideallsubsections]
 % Throughout your presentation, if you choose to use \section{} and \subsection{} commands, these will automatically be printed on this slide as an overview of your presentation
\end{frame}

@@

%------------------------------------------------
\subsection{Enforcing Local Stack Encapsulation using Capabilities} % A subsection can be created just before a set of slides with a common theme to further break down your presentation into chunks

\begin{frame}[fragile]
\frametitle{Capability Safety}
\textbf{Local State Encapsulation}
\\[1cm]
\begin{columns}[c]

\column{.45\textwidth} % Left column and width
\begin{tikzpicture}
    \node<1> (img1) {\includegraphics[scale=0.7]{images/wbcf_1.pdf}};
    \node<2> (img2) {\includegraphics[scale=0.7]{images/wbcf_2.pdf}};
    \node<3> (img3) {\includegraphics[scale=0.7]{images/wbcf_3.pdf}};
\end{tikzpicture}

@@

\foreach \i/\j in {1-1/5-1}
    \draw (a-\i) -- (a-\j);
%
\end{tikzpicture}
}
\uncover<3>{
\begin{center} well-bracketed \hspace{2cm} not well-bracketed \end{center}}

@@

\begin{frame}
\frametitle{Calling Convention}
\begin{tikzpicture}
    \node<1> (img1) {\includegraphics[scale=0.7]{images/calling_1.pdf}};
    \node<2> (img2) {\includegraphics[scale=0.7]{images/calling_2.pdf}};
\end{tikzpicture}

\begin{longtable}[c]{|l|l|}
\hline
\texttt{r\_stk} & $(RWLX,Local,b,e,a)$ \\ \hline
\endfirsthead
%
\endhead
\end{longtable}

@@

\begin{align*}
	a \mapsto_a[RWL] w \only<2->{&\fupd a \mapsto_a[RWL] ((p,Local),b,e,l) \\}
	\only<3->{&\fupd a \mapsto_a[RW] ((p,Local),b,e,l) \\}
	\only<4->{&\nfupd a \mapsto_a[RW] ((p',Local),b',e',l') \\}
\end{align*}

@@

\uncover<2->{
$$  \mathcal{V}\only<6->{{\color{red} (W)}}((\text{\tiny{RW}},g),b,e,a) \triangleq~ \bigsep_{a \in [b,e]} \fbox{$\exists w, a \mapsto_a [RW] w \sep \mathcal{V}\only<5->{{\color{red} (W)}}(w)$}$$}

@@

\begin{equation*}
\textsf{exec\_cond(W)(\textsf{p,g,b,e})} \triangleq \begin{cases}
\forall a \in [b~e], W' \sqsubseteq_{pub} W.\\
~\rhd~\mathcal{E}\interp{W'}{((p,g),b,e,a)} &g = Local\\ \\
\forall a \in [b~e], W' \sqsubseteq_{priv} W.\\
~\rhd~\mathcal{E}\interp{W'}{((p,g),b,e,a)} &g = Global\\
\end{cases}
\end{equation*}

@@

>>>>

\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{tikz}
\usetikzlibrary{matrix}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{IEEEtrantools}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage{longtable}
\usepackage{mathtools}
\usepackage{iris}

@@

%\newcommand{\ra}[1] {
%  \begin{tikzpicture}
%        \node[draw,dashed] {#1};
%    \end{tikzpicture}}

@@

%\begin{frame}
%\frametitle{Overview} % Table of contents slide, comment this block out to remove it
%\tableofcontents[hideallsubsections]
% % Throughout your presentation, if you choose to use \section{} and \subsection{} commands, these will automatically be printed on this slide as an overview of your presentation
%\end{frame}

@@

%------------------------------------------------
%\subsection{Enforcing Local Stack Encapsulation using Capabilities} % A subsection can be created just before a set of slides with a common theme to further break down your presentation into chunks
%
%\begin{frame}[fragile]
%\frametitle{Capability Safety}
%\textbf{Local State Encapsulation}
%\\[1cm]
%\begin{columns}[c]
%
%\column{.45\textwidth} % Left column and width
%\begin{tikzpicture}
%    \node<1> (img1) {\includegraphics[scale=0.7]{images/wbcf_1.pdf}};
%    \node<2> (img2) {\includegraphics[scale=0.7]{images/wbcf_2.pdf}};
%    \node<3> (img3) {\includegraphics[scale=0.7]{images/wbcf_3.pdf}};
%\end{tikzpicture}
%
%\column{.5\textwidth} % Right column and width
%\begin{center}
%\begin{lstlisting}
%push r_stk 1
%scall r 
%pop r_stk r_1
%assert r_1 1
%halt
%\end{lstlisting}
%\end{center}
%
%
%\end{columns}
%\end{frame}

@@

\foreach \i/\j in {1-1/5-1}
    \draw (a-\i) -- (a-\j);
%
\end{tikzpicture}
}

@@

\begin{frame}
\frametitle{Calling Convention}
\begin{tikzpicture}
    \node<1> (img1) {\includegraphics[scale=0.7]{images/calling_1.pdf}};
    \node<2> (img2) {\includegraphics[scale=0.7]{images/calling_2.pdf}};
\end{tikzpicture}
%
%\begin{longtable}[c]{|l|l|}
%\hline
%\texttt{r\_stk} & $(RWLX,Local,b,e,a)$ \\ \hline
%\endfirsthead
%%
%\endhead
%\end{longtable}

@@

\begin{align*}
	a \mapsto_a[RWL] w \only<2->{&\vs a \mapsto_a[RWL] ((p,Local),b,e,l) \\}
	\only<3->{&\vs a \mapsto_a[RW] ((p,Local),b,e,l) \\}
	\only<4->{&\not\vs a \mapsto_a[RW] ((p',Local),b',e',l') \\}
\end{align*}

@@

\uncover<2->{
$$  \mathcal{V}\only<6->{{\color{red} (\Sigma)}}((\text{\tiny{RW}},g),b,e,a) \triangleq~ \bigsep_{a \in [b,e]} \fbox{$\exists w, a \mapsto_a [RW] w * \mathcal{V}\only<5->{{\color{red} (\Sigma)}}(w)$}$$}

@@

\begin{equation*}
\textsf{exec\_cond($\Sigma$)(\textsf{p,g,b,e})} \triangleq \begin{cases}
\forall a \in [b~e], \Sigma ' \sqsupseteq_{pub} \Sigma.\\
~\rhd~\mathcal{E}\interp{\Sigma '}{((p,g),b,e,a)} &g = Local\\ \\
\forall a \in [b~e], \Sigma ' \sqsupseteq_{priv} \Sigma.\\
~\rhd~\mathcal{E}\interp{\Sigma '}{((p,g),b,e,a)} &g = Global\\
\end{cases}
\end{equation*}

@@

%------------------------------------------------
%\section{What's new/contributions}
%------------------------------------------------

\begin{frame}
\frametitle{What's new}

\textbf{What's new: capability machine viewpoint}

\begin{itemize}
	\item Mechanized formalization: currently $\sim 20,000$ lines of code
	\item A higher level of abstraction
\end{itemize}

~\\[1em]
\textbf{What's new: Iris formalization viewpoint}
\begin{itemize}
	\item Formalization of a machine level language, with no distinction between program and memory
	\item Distinction between  well-bracketed and non well-bracketed calls: using public/private transitions
\end{itemize}
